Price of Anarchy for Mean Field Games

### 2018-07-15 PoA.tex
Proposition 3 is completely finished

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

	% modification Main point 5 (nicolas)
	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
	\begin{equation}
		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	\begin{split}
	\text{when } A^u \neq 0,\qquad & u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u},\\
	\text{when } A^u = 0, \qquad & u_t^{r \to \infty} = D^{r \to \infty}_u + C^{r \to \infty}_u (T-t).
	\end{split}
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.

	Note that  $A^u \leq 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that for $r \geq r^*$, we have $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$. When $A^u \neq 0$, we have the following two inequalities for $r \geq r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + \zeta^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, for $A^u \neq 0$, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} } } \nonumber \\
		&=:&\kappa.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\bar{x}_t^{r,MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
	\end{equation*}
	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa ) T }, \quad t \in [0,T]. $$

>>>>

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$,
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

	% modification Main point 5 (nicolas)
	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
	\begin{equation}
		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that for $r \geq r^*$, we have $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$. We have the following two inequalities for $r \geq r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + \zeta^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} } } \nonumber \\
		&=:&\kappa.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\bar{x}_t^{r,MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
	\end{equation*}
	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa ) T }, \quad t \in [0,T]. $$
